---
title: "Exploratory Data Analysis of Diabetes Health Indicators"
format: html
---

## Introduction

This analysis aims to explore the Diabetes Health Indicators dataset to understand the relationships between various health indicators and the presence of diabetes. The ultimate goal is to use these insights to build predictive models.


## Data

Let's load the dataset and perform initial exploration.

```{r}
# Load the necessary libraries
library(tidyverse)

# Load the dataset
data <- read.csv("C:/Users/karen/Downloads/diabetes_binary_health_indicators_BRFSS2015.csv")

# Display the first few rows of the dataset
head(data)

```

## Data Cleaning and Transformation

We need to clean and transform the data for our analysis.

```{r}
# Convert relevant columns to factors
data <- data %>%
  mutate(across(where(is.numeric), as.factor))

# Check for missing values
sum(is.na(data))

```

## Summary Statistics

Let's generate summary statistics for the dataset.

```{r}
# Summary statistics for the dataset
summary(data)

```

## Visualizations

Let's create some visualizations to understand the relationships between variables.

```{r}
# Example visualization
ggplot(data, aes(x = factor(HighBP), fill = factor(Diabetes_binary))) +
  geom_bar(position = "dodge") +
  labs(title = "High Blood Pressure vs Diabetes", x = "High Blood Pressure", y = "Count", fill = "Diabetes")

```

[Click here for the modeling page](https://nishad-ncstate.github.io/Final_Project/Modeling.html)
