---
title: "Modeling Diabetes Health Indicators"
format: html
---

## Introduction

In this section, we will build and evaluate predictive models to classify individuals based on the Diabetes Health Indicators dataset.

## Data Split

First, we split the data into training and testing sets.

```{r}
# Load the necessary libraries
library(tidyverse)
library(caret)

# Load the dataset
data <- read.csv("C:/Users/karen/Downloads/diabetes_binary_health_indicators_BRFSS2015.csv")

# Convert Diabetes_binary to a factor with appropriate levels
data$Diabetes_binary <- factor(data$Diabetes_binary, levels = c(0, 1), labels = c("No", "Yes"))

# Set seed for reproducibility
set.seed(123)

# Split the data
train_index <- createDataPartition(data$Diabetes_binary, p = 0.7, list = FALSE)
train_data <- data[train_index, ]
test_data <- data[-train_index, ]
```

## Logistic Regression

Let's train and evaluate a logistic regression model.

```{r}
# Train Logistic Regression model
log_reg_model <- train(Diabetes_binary ~ ., data = train_data, method = "glm", family = "binomial", trControl = trainControl(method = "cv", number = 5, summaryFunction = mnLogLoss, classProbs = TRUE))

# Evaluate model performance
log_reg_model

```

## Classification Tree

Let's train and evaluate a classification tree model. 

```{r}
# Train Classification Tree model
tree_model <- train(Diabetes_binary ~ ., data = train_data, method = "rpart", trControl = trainControl(method = "cv", number = 5, summaryFunction = mnLogLoss, classProbs = TRUE), tuneGrid = expand.grid(cp = seq(0.01, 0.1, by = 0.01)))

# Evaluate model performance
tree_model

```

## Random Forest
